---
title: "Lab4"
author: "Cecilia Millane, Josh Zimmerman, Allie Tucker"
date: "3/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(readr)
av <- read.csv("http://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)

deaths <- av %>% gather(key = TimeD, value = Death, 11,13,15,17,19)

deaths <- deaths %>% mutate(TimeD = parse_number(TimeD))

returns <- ave %>% gather(key = TimeR, value = Return, 11:15)

returns <- returns %>% mutate(TimeR = parse_number(TimeR))

ave
```

What’s more, if you’re a fan of the MCU, nobody is safe. Of the nine Avengers we see on screen — Iron Man, Hulk, Captain America, Thor, Hawkeye, Black Widow, Scarlet Witch, Quicksilver and The Vision — every single one of them has died at least once in the course of their time Avenging in the comics. In fact, Hawkeye died twice!
- Although I was unable to find some of the superheros, I was able to verify that of the characters I could find, they all died at least twice, with Hawkeye dying twice

```{r}
deaths %>% filter(Name.Alias == 'Anthony Edward "Tony" Stark') %>% count(Death)

deaths %>% filter(Name.Alias == "Robert Bruce Banner") %>% count(Death)

deaths %>% filter(Name.Alias == 'Steven Rogers') %>% count(Death)

deaths %>% filter(Name.Alias == "Thor Odinson") %>% count(Death)

deaths %>% filter(Name.Alias == 'Clinton Francis Barton') %>% count(Death)

deaths %>% filter(Name.Alias == 'Wanda Maximoff') %>% count(Death)
```


**Out of 173 listed Avengers, my analysis found that 69 had died at least one time after they joined the team. **
  
  
```{r}
deaths %>% filter(TimeD==1) %>% count(Death)

deaths %>% filter(TimeD==1) %>% count()

```



**This shows that 69 had died at least once and that there are 173 Avengers.**
